\Title

### 2021-07-15 manuscript/content.tex
Fix small typos on manuscript

For ground surveys, the \emph{regular grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources below data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.
But when applied to airborne surveys, the \emph{sources below data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when griding airborne
magnetic data.
The \emph{regular grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

@@

\noindent
in which $z$ is the vertical coordinate (positive downwards) of an equivalent
source,
$\Delta z$ is a relative depth shift that is the same for all sources,
$\alpha$ is an adimensional depth factor,
$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
and
$z_{obs}$ is a vertical observation coordinate that will depend on the
horizontal layout strategy.
For \emph{sources below data}, it is the vertical coordinate of the data point
corresponding to the given source.
For \emph{regular grid}, it can be interpolated from the vertical coordinates
of all data points.
Finally, for \emph{block-averaged sources} it will be the median vertical
coordinate of the data within the corresponding block.

>>>>

For ground surveys, the \emph{regular grid} layout needs a sufficiently
small grid spacing to be able to fit the observed data.
This creates an unnecessarily large number of sources in areas where no
observations exist.
In contrast, the \emph{sources below data} layout is more likely to accurately
fit the observed data with many fewer sources, reducing the computational load.
But when applied to airborne surveys, the \emph{sources below data} layout may
place an undesirably large number of sources along the flight paths.
This could lead to aliasing effects on the predicted values, such as the
stripes parallel to flight lines that are often observed when gridding airborne
magnetic data.
The \emph{regular grid} layout can avoid this effect by evenly
distributing sources and using a continuous source layer (e.g.,
right-rectangular prisms or tesseroids).

@@

\noindent
in which $z$ is the vertical coordinate (positive downwards) of an equivalent
source,
$\Delta z$ is a relative depth shift that is the same for all sources,
$\alpha$ is an dimensionless depth factor,
$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
and
$z_{obs}$ is a vertical observation coordinate that will depend on the
horizontal layout strategy.
For \emph{sources below data}, it is the vertical coordinate of the data point
corresponding to the given source.
For \emph{regular grid}, it can be interpolated from the vertical coordinates
of all data points.
Finally, for \emph{block-averaged sources} it will be the median vertical
coordinate of the data within the corresponding block.
